\begin{thebibliography}{5}



\bibitem{biblio:spread_rumor}
Nick Fedewa, Emily Krause, Alexandra Sisson and Advisor: James Angelos.\\
\emph{Spread of A Rumor}.\\
\url{http://www.siam.org/students/siuro/vol6/S01182.pdf}

%First rumor paper found
\bibitem{biblio:stochastic_rumours} 
D. J. Daley, D. G. Kendall.
\emph{Stochastic Rumours}.\\
\url{http://imamat.oxfordjournals.org/content/1/1/42.abstract}

\bibitem{biblio:barabasilab_emergence}
A.-L. Barabási, R. Albert.
\emph{Emergence of scaling in random networks.}\\
\url{http://www.barabasilab.com/pubs/CCNR-ALB_Publications/199910-15_Science-Emergence/199910-15_Science-Emergence.pdf}

\bibitem{biblio:evolution_networks}
S. N. Dorogovtsev, J. F. F. Mendes.
\emph{Evolution of networks.}\\
\url{http://arxiv.org/pdf/cond-mat/0106144v2.pdf}

\bibitem{biblio:age_distribution_social}
Statista 2015.
\emph{Age distribution of active social media users worldwide as of 3rd quarter 2014, by platform }.\\
\url{http://www.statista.com/statistics/274829/age-distribution-of-active-social-media-users-worldwide-by-platform/}

\bibitem{biblio:fractal_resistant_disease} 
Zhongzhi Zhang, Shuigeng Zhou, Tao Zou, Guisheng Chen.
\emph{Fractal scale-free networks resistant to disease spread}.\\
\url{http://arxiv.org/pdf/0804.3186.pdf}

\bibitem{biblio:netlogo_dictionary} 
http://ccl.northwestern.edu.
\emph{NetLogo Dictionary}.\\
\url{http://ccl.northwestern.edu/netlogo/docs/dictionary.html}

\bibitem{biblio:graphstream} 
GraphStream Team.
\emph{GraphStream Project}.\\
\url{http://graphstream-project.org/}

\bibitem{biblio:graphml} 
GraphML Team.
\emph{The GraphML File Format}.\\
\url{http://graphml.graphdrawing.org/}

\bibitem{biblio:weibull}
Fritz Scholz.
\emph{Inference for the Weibull Distribution}.\\
\url{http://www.stat.washington.edu/fritz/DATAFILES498B2008/WeibullBounds.pdf}


\end{thebibliography}